%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Authors:
% Tom konidas (tomkonidas@protonmail.ch)
%
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Tom}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Konidas}}}}} % Last name
	
	\vspace{6pt}
	
	{\huge Software Developer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{Monreal}\\
	\icon{Phone}{12}{+1 514 261-5772}\\
	\icon{At}{12}{\href{mailto:tomkonidas@pm.me}{tomkonidas@pm.me}}\\	
	\icon{Skype}{12}{tomkonidas}\\
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Globe}{12}{\href{https://tomkonidas.com}{tomkonidas.com}}\\
	\icon{Github}{12}{\href{https://github.com/tomkonidas}{github.com/tomkonidas}}\\
	\icon{Linkedin}{12}{\href{https://www.linkedin.com/in/tomkonidas/}{tomkonidas}}\\
	\icon{Twitter}{12}{\href{https://twitter.com/tomkonidas/}{@tomkonidas}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Who Am I?}

\begin{minipage}[t]{0.4\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
  Hello, my name is Tom Konidas and I'm a minimalist who truly believes that less is more. 
  My passions are Software Development, Cybersecurity, Free and Open Source Software and the communities that surround them.
  I love knowledge and I strongly believe technology can, and should, enrich every single 
  life our universe has to offer.
  You can catch me at the Montreal Elixir Meetup.
  I am currently studying for my CCNA and Bachelor of Computer Science.
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5.5}
		\baritem{ReactJS}{100}
		\baritem{NodeJS/Express}{90}
        \baritem{Java}{80}
		\baritem{REST/Postman}{75}
		\baritem{SQL/NoSQL}{90}
		\baritem{GNU/Linux/Bash}{85}
	\end{barchart}
\end{minipage}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{1/2019 -- Present\\\footnotesize{Full Time}}
		{Full-Stack Developer}
		{Fix Network}
		{Developed an internal e-commerce platform.\\
      Developed \& designed an internal careers admin page connecting all the umbrella brands.\\
      Created custom software and tools to better help employees and franchisees.\\
      Generated automatic reports querying large data for helpful insights.\\ 
      Maintained public corporate sites for over 500 shops worldwide.
      \\\texttt{Sncode}\slashsep\texttt{Extenso}\slashsep\texttt{MariaDB}\slashsep\texttt{jQuery}\slashsep\texttt{Bootstrap}\slashsep\texttt{Git}}
	\entry
		{6/2017 -- Present\\\footnotesize{Freelance}}
		{Software Developer}
		{tomkonidas.com}
		{Generated blazing fast websites using SSG and SSR technologies.\\
      Built simple yet elegant UI/UX solutions catered to the customers needs.\\
      Performed SEO optimizations helping customers get on the first page google results.\\
      Developed variety of projects ranging from full-stack applications to blogs \& landing pages.\\
      Provided maintenance and cost-efficient hosting services.
      \\\texttt{React}\slashsep\texttt{VueJS}\slashsep\texttt{Node}\slashsep\texttt{Express}\slashsep\texttt{MongoDB}\slashsep\texttt{Git}}
	\entry
		{1/2018 -- 12/2018\\\footnotesize{Full Time}}
		{Application Support Analyst}
		{Tecsys Inc.}
		{Improved database performance using SolarWinds, JavaMelody and Nagios.\\
      Applied patches to large codebase and installed on all customers' environments.\\
      Obtained 'Pat on the back' award from customer for going beyond and beyond my responsibilities.\\
      Reproduced bugs and logged tickets to R\&D.\\
      Provided on-site support for customers.
      \\\texttt{Java}\slashsep\texttt{MS SQL}\slashsep\texttt{Agile SCRUM}\slashsep\texttt{SVN}}
	\entry
		{9/2017 -- 12/2017\\\footnotesize{Internship}}
		{Engineering/Marketing}
		{Ranger Design}
    {Hired as the link between Engineering and Marketing to work on the Ranger Design Configurator.\\
      Optimized Meshes in Rhino5/Blender decreasing load times on the website.\\
      Created and edited CAD layouts in Solidworks helping customers visualize their custom orders.\\
      Documented product changes within ERP (Infor SyteLine). 
      \\\texttt{Blender}\slashsep\texttt{SolidWorks}\slashsep\texttt{Rhino5}}
	\entry
		{4/2016 -- 9/2017\\\footnotesize{Full Time}}
		{Data Administrator / Systems Administrator}
		{CVM PK Auto}
    {Implemented a live local appointment system using Google Sheets.\\
      Resolved all issues related to computers, printers and networks.\\
      Crafted a modern, easy to navigate website.\\
      Developed python scripts to manipulate excel sheet data.\\
      Set up new Windows environments for new hires.
      \\\texttt{Python}\slashsep\texttt{MS Suite}\slashsep\texttt{HTML/CSS/JS}\slashsep\texttt{Photoshop}}
	\entry
		{1/2015 -- 5/2015\\\footnotesize{Internship}}
		{Full-Stack Developer}
		{Booxi}
    {Developed an admin panel (CRUD) using Google's Web Toolkit (GWT) and python back-end.\\
      Coded web-scraping scripts (Python BeautifulSoup Library) gathering potential customers.\\
      Contributed to large codebase and learned how to work with git repositories within a team.
      \\\texttt{Java}\slashsep\texttt{Python}\slashsep\texttt{MySQL}\slashsep\texttt{REST}\slashsep\texttt{GWT}\slashsep\texttt{Git}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2020 -- Present}
		{Bachelor of Computer Science}
		{Concordia University}
		{Part-Time}
	\entry
		{2012 -- 2015}
		{DEC in Computer Science \& Technology}
		{Vanier College}
		{}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\cvsect{Projects}

\begin{entrylist}
	\entry
		{Personal Website}
		{tomkonidas.com}
		{}
		{Generated blazing fast static website with SSG technology using Grdisome.\\
      Integrated Dark and Light modes with custom layout and designs.\\
      Uses serverless functions to power the contact form.\\ 
      Near 100\% score in Google Lighthouse audit report.
      \\\texttt{VueJS}\slashsep\texttt{Gridsome}\slashsep\texttt{TailwindCSS}\slashsep\texttt{Netlify}}

	\entry
		{Passion Project}
		{pebl}
		{}
		{A FOSS invoice generator App made in Elixir/Phoenix.\\
      Full CI/CD And TDD workflow with mix tests and travis-ci.\\
      Invoice creation with live view and PDF export.\\ 
      User profiles that store brand information for a customized invoice.
      \\\texttt{Elixir}\slashsep\texttt{Phoenix}\slashsep\texttt{TailwindCSS}\slashsep\texttt{PostgreSQL}\slashsep\texttt{Docker}\slashsep\texttt{CI/CD}}

	\entry
		{Client Work}
		{Sell Your Listings}
		{}
		{A Web App for Real Estate client services.\\
      Server-Side rendered app for improved performance and SEO.\\
      Fully modular design with React components.\\
      Developed a build-your-own Services Pricing feature.\\ 
      Building a dashboard where the client can update/edit the content.
      \\\texttt{ReactJS}\slashsep\texttt{NextJS}\slashsep\texttt{TailwindCSS}\slashsep\texttt{NodeJS}\slashsep\texttt{ExpressJS}\slashsep\texttt{Mongo}}

	\entry
		{Personal Blog}
		{konidas.net}
		{}
		{My own Personal Tech blog built in Go/Hugo.\\
      Generate Static Blog content via Markdown files.\\
      Build in SEO and asset optimizations.\\
      Automatic builds when pushed/merged git commits to master.\\
      Developed custom HTML/CSS/JS templates for pages and posts.
      \\\texttt{Go}\slashsep\texttt{Hugo}\slashsep\texttt{Markdown}\slashsep\texttt{Netlify}\slashsep\texttt{git}}

	\entry
		{Client Work}
		{Cowboy Meets Pirate}
		{}
		{Official Website for Canadian Rock band Cowboy Meets Pirate.\\
      Static Site Generation with Gatsby/ReactJS.\\
      Lazy Loading content and Asset optimizations.\\
      Mailchimp Email subscribe form.\\
      Fully Mobile/Tablet/Desktop Responsive design.
      \\\texttt{ReactJS}\slashsep\texttt{Gatsby}\slashsep\texttt{Netlify}\slashsep\texttt{Git}}

\end{entrylist}
\begin{minipage}[t]{0.2\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}
	
	\textbf{English} - native\\
	\textbf{French} - proficient\\
	\textbf{Greek} - rudimentary
\end{minipage}
\hfill
\begin{minipage}[t]{0.4\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Hobbies}
	
    Playing around with networks and hardware (Raspberry Pi).
  Discovering new podcasts and listening/viewing to conference talks.
  Producing music,videos and graphic art.
  Keeping up to date with FOSS and Hacker culture.
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Non profit}
	
	I help run the local Montreal Elixir Meetup by recording the talks and edit/post them online.
\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
